P3692R2: How to Avoid OOTA Without Really Trying

### 2025-07-11 paper/ootavacuous.tex

In short, this paper's contribution is to show how these
constraints allow real-world C++ implementations doing per-thread
analysis to avoid OOTA behavior easily,
%and not with minimal cost~\cite{PiezhaoOu2018OOTApapl},
in many cases with no cost at
all~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying}.
In addition, our results simplify the job of researchers seeking
practical impact by allowing them ignore C++ implementers' need for
extreme simplicity and performance.
This in turn permits such researchers to focus on advanced topics such
as formal-verification tooling and evaluation of optimizations.
% \emph{@@@ Are these the right qualifiers?}

>>>>

In short, this paper's contribution is to show how these
constraints allow real-world C++ implementations doing per-thread
analysis to avoid OOTA behavior easily,
%and not with minimal cost~\cite{PiezhaoOu2018OOTApapl},
in many cases with no cost at
all~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying}.
In addition, our results simplify the job of OOTA researchers seeking
practical impact by allowing them to ignore C++ implementers' need for
extreme simplicity and performance.
This in turn permits such researchers to focus on advanced topics such
as formal-verification tooling and evaluation of optimizations.
% \emph{@@@ Are these the right qualifiers?}
